### 2014-04-16 doc/uist14/iteration2.tex
iteration2: grammar/minor content updates

%With our first study, we learn that using IR to perform {\em coarse selection} can reduce the overall target selection time. A major reason for the improvement is because disambiguation is only needed 10\% of the time. 
%because in many cases there will be only one target in range and fine selection is not needed, and in cases where it’s needed, the list length has been effectively reduced. 
Performance of the {\em Naive IR} technique will degrade as target density in an environment increases, as increased density will require refinement steps. We therefore ask a follow-on research question: {\em``How might we improve selection time in a dense environment?''}

\subsection{Technique}
Previously we only used IR reception as a binary signal for identifying potential targets. We hypothesize that IR intensity at the receiver side can provide more information about the likelihood that a user intended to select a particular target. Received IR intensity falls off with distance between IR emitter and receiver as well as with the angle between emitter and receiver. To measure intensity, we add an IR light-to-voltage converter TSL267-LF by AMS-TAOS USA Inc.
% transmitter webpage: http://www.digikey.com/product-search/en?x=0&y=0&lang=en&site=us&KeyWords=475-2919-ND
% http://www.digikey.com/product-detail/en/TSL267-LF/TSL267-LF-ND/3095052

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/IRIntensityDistribution.pdf}
\caption{Empirical measurement of IR intensity at different position. We measure the intensity at the plane of every 1 meter away from the IR emitter. On that plane, we obtain a sample every 5 centimeters. The size and color brightness in this graph represents the intensity readings.}
\label{fig:measurement}
\end{figure}

The intensity information is used in two ways:
\begin{enumerate}
\item When multiple targets have received IR signals and reported the intensity readings, we discard those whose intensities are significantly lower than the largest reading\footnote{In our current implementation, we empirically set it to be half of the ADC resolution, which is frequently used because it indicates a 3dB loss in the signal strength.}. Therefore, when there is only one target within line of sight, the IR intensity approach has the same behavior as the previous iteration - no disambiguation is needed. When the environment turns denser, the new design can filter some peripheral targets out, reducing $P(refine)$, the likelihood of entering the refinement stage.
\item When refinement is still needed, meaning that multiple targets have relatively close intensity values, the system sorts the disambiguation list according to the IR intensity, from strongest to weakest. We hypothesize that this will reduce time $t_{refine}$ significantly by minimizing extra navigation steps. (Ideally, the first list item will match the actual, intended target.)
\end{enumerate}

@@

In the cases when disambiguation is inevitable, {\em Intensity IR} sorts the list based on the intensity reading, while {\em Naive IR} sorts alphabetically. {\em Intensity IR} reduces the fraction of refinement trails in which additional list navigation is necessary (i.e., the first, already selected element is incorrect).  {\em Intensity IR} sorted the desired target as the first one in the list in 55\% of cases (93 of 167). In comparison, for {\em Naive IR}, only 35\% of trials sorted the desired target as the first one in the list (80 out of 225). A Chi-square test show that this difference is significant (with $\chi^2(1) = 15.758$, $p < 0.0001$).

>>>>

%With our first study, we learn that using IR to perform {\em coarse selection} can reduce the overall target selection time. A major reason for the improvement is because disambiguation is only needed 10\% of the time. 
%because in many cases there will be only one target in range and fine selection is not needed, and in cases where it’s needed, the list length has been effectively reduced.

Performance of the {\em Naive IR} technique will degrade as target density in an environment increases, as increased density will require refinement steps. We therefore ask a follow-up research question: {\em``How might we improve selection time in a dense environment?''}

\subsection{Technique}
Previously we only used IR reception as a binary signal for identifying potential targets. We hypothesize that IR intensity at the receiver side can provide more information about the likelihood that a user intended to select a particular target. Received IR intensity falls off with distance between IR emitter and receiver as well as with the angle between the emitter and receiver. To measure intensity, we add an IR light-to-voltage converter TSL267-LF by AMS-TAOS USA Inc.

% transmitter webpage: http://www.digikey.com/product-search/en?x=0&y=0&lang=en&site=us&KeyWords=475-2919-ND
% http://www.digikey.com/product-detail/en/TSL267-LF/TSL267-LF-ND/3095052

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/IRIntensityDistribution.pdf}
\caption{Empirical measurement of IR intensity at different position. We measure the intensity at a plane every meter away from the IR emitter. On that plane, we obtain a sample every 5 centimeters. The size and color brightness in this graph represents the intensity readings.}
\label{fig:measurement}
\end{figure}

The intensity information is used in two ways:
\begin{enumerate}
\item When multiple targets have received IR signals and reported the intensity readings, we discard those whose intensities are significantly lower than the largest reading\footnote{In our current implementation, we empirically set it to be half of the ADC resolution, which is frequently used as it indicates a 3dB loss in the signal strength.}. Therefore, when there is only one target within line of sight, the IR intensity approach has the same behavior as the previous iteration - no disambiguation is needed. When the environment turns denser, the new design can filter some peripheral targets out, reducing $P(refine)$, the likelihood of entering the refinement stage.
\item When refinement is still needed, meaning that multiple targets have relatively close intensity values, the system sorts the disambiguation list according to the IR intensity, from strongest to weakest. We hypothesize that this will reduce $t_{refine}$ significantly by minimizing extra navigation steps, as the first list item will generally match the intended target.
\end{enumerate}

@@

In the cases where disambiguation is inevitable, {\em Intensity IR} sorts the list based on the intensity reading, while {\em Naive IR} sorts alphabetically. {\em Intensity IR} reduces the fraction of refinement trails in which additional list navigation is necessary (i.e., the first, already selected element is incorrect).  {\em Intensity IR} sorted the desired target as the first one in the list in 55\% of cases (93 of 167). In comparison, for {\em Naive IR}, only 35\% of trials sorted the desired target as the first one in the list (80 out of 225). A Chi-square test show that this difference is significant (with $\chi^2(1) = 15.758$, $p < 0.0001$).
